Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-23 lloveras_2020.tex
cambios varios en figuras y texto

\address[id=aff2]{Universidad Nacional de Tres de Febrero (UNTREF), Valent\'{\i}n G\'omez 4752, (B1678ABH) Caseros, Provincia de Buenos Aires, Argentina}

@@

While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $310\mdeg$ \diego{and }. Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature. In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.

@@

\temp{aca se defininen los highpoints, se comentan los colores y enunciar que cada uno puebla una regino termodinamica diferente}

@@

\temp{Aca una linea que linkea la definicion del tipo de lineas en la seccion anterior con las regiones que se ven en la figura que se describe a continuacion}

As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down {loops} in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type I lines, populating all the streamer but mostly the mid latitudes. In red the type II lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type 0 (cyan), I (blue), II (red) and III (green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of {legs}. \notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors. I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet. In this way, blue will be DOWN loops and red will be UP loops, as in previous papers. The same change applies to Figure 4. Also, how about making Figures 3 and 4 a single Figure of four panels? Just an idea.} }
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\diego{Comienza la energia}\\

@@

To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}. In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria. Now the type 0 loops are down loops.

@@

The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures. The differences

We found larger temperature gradients for CR2208 than CR2082, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations. Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.

@@

A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well. The closed region is denser and hotter than the open region. The density and temperature gradients are maximum in the open-close boundary. The open field regions in low latitudes maintain thermodynamic values associated with open regions. CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \temp{estoy asumiento que es una AR}. In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.

@@

\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}

@@

The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
As a way to understand the distribution of the selected lines, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In blue the type I lines, populating mostly the entire streamer. In red the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.

@@

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
\label{rpoint_awsom}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

@@

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.

*Down loops, shiff y cranmer comentarios.

*Energia DEMT\\
We can see, on type 0 loops, a median value of energy input flux for CR2082 twice bigger than CR2208. Also, in both rotations, we observe a negative population of loop integrated energy input flux. This can refer to some loops where loop-integrated radiative flux is too small in comparison with the larger gradients of negative conductive flux, resulting in negative energy input flux.

This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power. Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.  Bottom panels show the comparison for larger type I loops.

>>>>

\address[id=aff2]{Universidad Nacional de Tres de Febrero (UNTREF). Departamento de Ciencia y Tecnolog\'{\i}a, Sáenz Peña, Argentina.}

@@

While CR-2082 was highly axisymmetric and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$. CR-2208 showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$. Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature. In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.

@@

@@

\diego{
As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded. At top, all traced legs with enaugh tomographic data are shown. In black all legs corresponding to closed lines and in grey corresponding to open lines. This traced lines were divided into four types as explained in Section \ref{trace} and the fit in density and temperature was applied, selecting only those legs that met the criteria. The bottom figure shows the latitudinal-longitudinal location of this selected lines at same height. In blue the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down legs). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down legs in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down legs in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In red the type I lines, populating all the streamer but mostly the mid latitudes. In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\diego{At the top, latitude-longitude location of all open (grey) and closed (black) lines traced. At the bottom, latitude-longitude location of each leg that was traced and that meets the criteria listed in Section \ref{trace}. Type 0, I, II and III are shown in blue, red, violet and green respectively at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of {legs}.} \notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.} }
\label{rpoint_demt}
\end{center}
\end{figure}

@@

@@

To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}. In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria. When two legs of the same loop have a decreasing temperature with height (type 0), they are called down loops.

@@

The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures. The conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations. Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.

@@

A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well. The closed region is denser and hotter than the open region. The density and temperature gradients are maximum in the open-close boundary. The open field regions in low latitudes maintain thermodynamic values associated with open regions. The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$. In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.

@@

%\temp{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}

@@

The actual version of the AWSoM model can not reproduce down legs, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.

As a way to understand the distribution of legs, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the traced legs at top and the selected fitted legs meeting the criteria at $1.105\,\mrsun$ for both rotations, in the same way as in Section \ref{demt_res}. In red the type I lines, populating mostly the entire streamer. In violet the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_awsom_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_awsom_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
\label{rpoint_awsom}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\diego{aca podria ir un pequeño parrafo que resuma las diferencias. Pero justo a continuacion empiezan las conclusiones y uno tiende a repetir, no se como encararlo para que no quede dos veces lo mismo y tan pegado uno de lo otro.}

@@

\diego{NOTE: Here is a paragraph describing the empirical successes in the reconstruction of both rotations.}

*In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.

*Coronal magnetic structures for which the temperature increases/decreases with height in the range of heights covered by DEMT, $1.02–1.22\,\mrsun$, have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first observed their presence by means of DEMT. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study by \citet{schiff_2016}, down and up loops have been successfully reproduced by a numerical implementation of a 1D steady-state model that considers time-averaged heating rates.

We found down legs in the DEMT reconstructions mainly in the equatorial latitudes, being a greater quantity and better distribution along longitudes in CR-2082 than in CR-2208. \citet{nuevo_2013} showed a decrease in the amount of down loops as the solar activity increases, which is consistent with the results shown in this article.

*We can see, on type 0 loops, a median value of energy input flux ($\phi_h$) for CR-2082 twice bigger than CR-2208. In both rotations this magnitude has negative values, this can refer to some loops where loop-integrated radiative flux $\phi_r$) is too small in comparison with the larger gradients of negative conductive flux $\phi_c$), resulting in negative energy input flux.

This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power. Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.

Consistent that the density in CR-2082 was higher, the $\phi_r$ was also higher. In both rotations the magnitudes in the temperature gradients are similar, but the temperatures in CR-2208 were consistently higher at all heights, resulting in a larger $\phi_c$ in module. This results are in agree with the observations of \citet{maccormack_2017}.

\diego{THE AR of CR-2082 wasn't well modeled by AWSoM.}

In both rotations, AWSoM and DEMT resutls shows same termodynamic structures along latitude and longitude with very comparable values between $1.055 - 1.25\,\mrsun$

Figure \ref{histos_2082} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2082 was found to be less dense $\approx 11-22\%$ and colder $\approx 5-10\%$.

Both reconstructions of CR-2208 reconstructed the ARs with very similare values and in almost the same latitude-longitude location. Figure \ref{histos_2208} and Table \ref{tabla_comp} indicate that AWSoM reconstruction of CR-2208 was found to be denser $\approx 0-10\%$ and colder $\approx 10-15\%$.

CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.

\diego{I would like to say something about FIgure 10. Maybe the weird tale in AWSoM Ne in the poles. Ideas?}\\

\diego{We could say something about the anti correlation between speed and density and not get into the trace because issues do always appear and we don't have much time, and we all want to be happy in january. Unless the collaborators find easy to make this part.}
